Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-01-31 paper/main.Rmd
updating materials
added what I learnt from simulation

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
here::here()
read_chunk(here::here("paper/R/", "null_distribution.R"))
read_chunk(here::here("paper/R/", "mean_null.R"))
source(here::here("paper/R/sim_panel.R"))
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

@@

The tabulated values and graphical representations of the simulation results are provided in Appendix. The learning from the simulations are as follows:

## Properties

>>>>

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
here::here()
#knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
#knitr::read_chunk(here::here("paper/R/", "mean_null.R"))
#source(here::here("paper/R/sim_panel.R"))
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

@@

The tabulated values and graphical representations of the simulation results are provided in Appendix. The learning from the simulations are as follows:
The values of the measure $wpd_{raw}$ is least for $D_{null}$, followed by 
$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$). This is a desirable result since the measure $wpd_{raw}$ was designed such that this relationship holds.
Furthermore, the distribution of the measure $wpd_{raw}$ changes for different facet and x categories. The location of the distribution shifts to the right and it also becomes more skewed for more higher facet and x-axis categories. Now this is not desirable, as it would mean that we can't compare the $wpd_{raw}$ values across different panels. The distribution of $wpd_{norm}$ looks more similar with at least the mean and standard of the distributions being uniform across panels. This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels. Also, note that since the data is processed using normal-quantile-transform, this measure is independepent of the intial distribution of the underlying data and hence is also comparable across different datasets. This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100. More detailed results about the properties of $wpd_{raw}$ and $wpd_{norm}$ could be found in Appendix.
